Numerical simulation of the Cordilleran ice sheet \\ through the last glacial cycle

### 2014-06-26 kappa.tex
Add projection parameters table.

\todo{Figure. Location map of North America}\\
\todo{Figure. Topographic map of the Cordillera}\\
\todo{Table. LCC projection parameters?}

>>>>

\todo{Figure. Location map of North America}\\
\todo{Figure. Topographic map of the Cordillera}\\

\begin{table}
  \centering
  \caption{Properties of the Canadian Atlas Lambert conformal conic projection
           (EPSG code~3978) and the GRS~1980 ellipsoid, and corresponding
           PROJ.4 parameter names, as used in all model runs, ice volume and
           area calculations, and most figures.}
  \label{tab:projparams}
  \makebox[0pt]{\begin{tabular*}{80mm}{@{\extracolsep{\fill}}lcc}
    \hline
    Parameter               & Name              & Value \\
    \hline
    Projection name         & \texttt{+proj}    & \texttt{lcc} \\
    Central meridian        & \texttt{+lon\_0}  & 95\degree W \\
    Latitude of origin      & \texttt{+lat\_0}  & 49\degree N \\
    First secant parallel   & \texttt{+lat\_1}  & 49\degree N \\
    Second secant parallel  & \texttt{+lat\_2}  & 77\degree N \\
    Semimajor radius        & \texttt{+a}       & 6378137\,m \\
    Reciprocal flattening   & \texttt{+rf}      & 298.257222101 \\
    \hline
  \end{tabular*}}
\end{table}
